Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-19 paper-v1.tex
update implementation by @naszam

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{Kovan Testnet}.\textsc{URL:}https://kovan.etherscan.io/.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \begin{itemize}
     \item \emph{upload of the files} containing the requirements of the peer-review and the paper to be reviewed into IPFS, whose hash is stored into the Ethereum blockchain as PoE;
     \item \emph{specification of a deadline} in the form of a UNIX timestamp after which the fulfillment will no longer be accepted;
     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer-reviews sent by the peer-reviewers;
\end{itemize}
 Bob (peer-reviewer) downloads the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
If Alice does not receive any peer-review, she cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[9]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.

@@

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[10]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[11]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community). zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[12]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
\subsection{Future developments}
The Ants-Review Protocol will make the following integrations.
An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens. Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[13]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[14]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[15]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[16]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few. 
In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.
This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants. This will allow to incentives prolific peer-peviewers and research and improve the stability of the system together with ideally a reward system to rank the best peer-reviewers.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}

>>>>

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{Kovan Testnet}.\textsc{URL:}https://kovan.etherscan.io/.}. AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \begin{itemize}
     \item \emph{upload of the files} containing the requirements of the peer-review and the paper to be reviewed into IPFS, whose hash is stored into the Ethereum blockchain as PoE;
     \item \emph{specification of a deadline} in the form of a UNIX timestamp after which the fulfillment will no longer be accepted;
     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer-reviews sent by the peer-reviewers;
\end{itemize}
 Bob (peer-reviewer) downloads the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
If Alice does not receive any peer-review, she cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.

@@

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community). zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
\subsection{Future developments}
The Ants-Review Protocol will make the following integrations.
An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens. Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[15]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few. 
In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.
This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants. This will allow to incentives prolific peer-peviewers and research and improve the stability of the system together with ideally a reward system to rank the best peer-reviewers.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}
